Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
legendes des tables

\subsection{Precision of the various techniques}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}}
& \multicolumn{3}{c|}{\textbf{DIS/G+PF}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subsetneq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants better with the right-side technique,
and ``unc.'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage.}
\label{tab:techniques}
\end{table*}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{OCT/PKEQ}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF).}
\label{tab:time}
\end{table*}

>>>>

\subsection{Precision of the various techniques}
\label{sec:compare_techniques}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}}
& \multicolumn{3}{c|}{\textbf{DIS/G+PF}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), our combined technique (G+PF), and its version using
disjunctive invariants (DIS). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subsetneq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants better with the right-side technique,
and ``unc.'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage.}
\label{tab:techniques}
\end{table*}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{OCT/PKEQ}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF). We used as abstract domains Convex Polyhedra (PK),
Octagons (OCT), intervals (BOX) and linear equalities (PKEQ).}
\label{tab:domain}
\end{table*}

For each program and each pair $(D_1,D_2)$ of abstract domains, we compare by
inclusion the invariants of the different control points in $P_R$ (where $P_R$
is defined as in \ref{sec:compare_techniques}).
The detailed results are given in Table \ref{tab:domain}.
